Blocking-resistant communication\\through domain fronting

### 2014-07-30 docs/meek.tex
Misc. revisions.

Figure~\ref{fig:ciphersuites} shows examples of how TLS client
implementations may differ.
Figure~\ref{fig:ciphersuites:golang} is from the Go programming languages
built-in net/http library~\cite{golang-net/http},
which has a custom TLS implementation;
it is how \meekclient\ would appear with no TLS camouflage.
It is unlike Figures~\ref{fig:ciphersuites:firefox} and~\ref{fig:ciphersuites:chrome},
which are browsers; the browsers are also unlike each other.
A censor could block an uncamouflaged \meek using Go's fingerprint,
if it considered the collateral damage resulting from blocking other Go programs to be slight enough.

@@

Fastly (\url{http://www.fastly.com/}) is a CDN.
It is unique among the the services we tested in that
it is the only one that appears to enforce the SNI:
if the SNI and Host do not match,
the Fastly edge server returns an HTTP 400 error.
It is thus the only service we have found
for which the ``domainless'' fronting style is required.

@@

The issue of statistical traffic anaysis is a general one~\cite{trafficmorphing},
and mostly orthogonal to \meek's main idea, domain fronting.
It may be that the problem is
best solved by a modular component not
specifically designed for \meek.

% Advantage is that we are probably proxying web traffic.
As \meek is based on HTTPS,
we compare traffic traces of \meek against
traces of ``ordinary'' HTTPS traffic.
We did a packet capture
automatically browsing the home pages
of the top 500 Alexa web sites using \meek,
with a firewall in place so that no extraneous traffic was included.
The used \meek in Tor Browser,
with the browser camouflage described in Section~\ref{sec:browserextension},
and Google App Engine as the intermediate web service.
The \meek trace is 687~megabytes in all.
Our representative of ordinary HTTPS traffic
is a sanitized trace of 10 minutes of HTTPS traffic
% anon
from Lawrence Berkeley National Laboratory (LBL),
comprising data to and from TCP port 443 on any Google server.
% Mention the non-google if it appears in a figure.
The trace contains packet headers only, not payloads
were replaced by an incrementing counter.
The LBL trace consists 313~megabytes of packet headers,
not payloads, destined for TCP port 443 on any Google server.
The original IP addresses were masked by being
replaced by a counter before we received the trace.

>>>>

Figure~\ref{fig:ciphersuites} shows examples of how TLS client
implementations may differ.
\meekclient\ is written in the Go programming language,
which has a custom TLS library~\cite{golang-crypto/tls};
Figure~\ref{fig:ciphersuites:golang}
shows how it would appear with no TLS camouflage.
Figures~\ref{fig:ciphersuites:firefox} and~\ref{fig:ciphersuites:chrome},
which are browsers, are different; the browsers are also unlike each other.
A censor could block an uncamouflaged \meek using Go's fingerprint,
if it considered the collateral damage resulting from blocking other Go programs to be slight enough.

@@

Fastly (\url{http://www.fastly.com/}) is a CDN.
It is unique among the the services we tested in that
it is the only one that appears to enforce the SNI:
if the SNI and Host do not match,
the Fastly edge server returns an HTTP 400 error.
It is the only service we have found
that requires the ``domainless'' fronting style.

@@

The issue of statistical traffic anaysis is a general one~\cite{trafficmorphing},
and mostly orthogonal to \meek's main idea, domain fronting.
It may be that the problem is
best solved by a modular component not
necessarily specifically designed for \meek.

% Advantage is that we are probably proxying web traffic.
As \meek is based on HTTPS,
we compare traffic traces of \meek against
traces of ``ordinary'' HTTPS traffic.
We did a packet capture
automatically browsing the home pages
of the top 500 Alexa web sites using \meek,
with a firewall in place so that no extraneous traffic was included.
The used \meek in Tor Browser,
with the browser camouflage described in Section~\ref{sec:browserextension},
and Google App Engine as the intermediate web service.
The \meek trace is 687~megabytes in all
and covers about 4.5 hours of network activity.
Our representative of ordinary HTTPS traffic
is a sanitized trace of 10 minutes of HTTPS traffic
% anon
from Lawrence Berkeley National Laboratory (LBL),
comprising data to and from TCP port 443 on any Google server.
% Mention the non-google if it appears in a figure.
The trace contains packet headers only, not payloads
were replaced by an incrementing counter.
The LBL trace consists 313~megabytes of packet headers,
not payloads, destined for TCP port 443 on any Google server.
The original IP addresses were masked by being
replaced by a counter before we received the trace.
